Differences in care for patients experiencing left vs. right hemisphere ICH

### 2024-02-16 reports/priors.qmd
aggressive priors complete?
still having issues with vent model

# load targets objects
tar_load(model_parameters)
tar_load(prior_neurosurgery_minimal)
tar_load(prior_neurosurgery_canonical)
tar_load(prior_evd_minimal)
tar_load(prior_evd_canonical)

@@

  p2 <- predictions(y, by = "ich_laterality") |>
    as_tibble()

  p3 <- avg_comparisons(y, variables = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw)) +
    stat_halfeye(
      .width = c(0.8, 0.95), point_interval = "median_hdi",
      fill = "#bc3032"
    ) +
    scale_x_continuous(labels = label_pp) +
    labs(
      title = "Prior Predictive Check",
      x = paste("Effect of hemispheric laterality\n on the probability of", {{ var }}),
      y = NULL, caption = "80% and 95% credible intervals shown in black"
    )

  return(list(
    priors = p1,
    predictions = p2,
    plot = p3
  ))
}

@@

prior_neurosurgery_minimal

@@

>>>>

# load targets objects
tar_load(model_parameters)
tar_load(prior_neurosurgery_minimal)
tar_load(prior_neurosurgery_canonical)
tar_load(prior_evd_minimal)
tar_load(prior_evd_canonical)
tar_load(prior_trach_minimal)
tar_load(prior_trach_canonical)
tar_load(prior_vent_minimal)
tar_load(prior_vent_canonical)

@@

  p2 <- y

  p3 <- predictions(y, by = "ich_laterality") |>
    as_tibble()

  p4 <- avg_comparisons(y, variables = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw)) +
    stat_halfeye(
      .width = c(0.8, 0.95), point_interval = "median_hdi",
      fill = "#bc3032"
    ) +
    scale_x_continuous(labels = label_pp) +
    labs(
      title = "Prior Predictive Check",
      x = paste("Effect of hemispheric laterality\n on the probability of", {{ var }}),
      y = NULL, caption = "80% and 95% credible intervals shown in black"
    )

  return(list(
    priors = p1,
    model = p2,
    predictions = p3,
    plot = p4
  ))
}

@@

@@

### Tracheostomy

prior_printing("trach_minimal", prior_trach_minimal, "receiving an tracheostomy")

prior_printing("trach_canonical", prior_trach_canonical, "receiving a tracheostomy")

### Days of Mechanical Ventilation

prior_printing("vent_minimal", prior_vent_minimal, "number of days of mechanical ventilation")

prior_printing("vent_canonical", prior_vent_canonical, "number of days of mechanical ventilation")
